\papertitle

### 2013-02-05 manuscript.tex
edits

In this section, we present the numerical results of the experiments we used to 
determine the values of the parameters in our system model.

>>>>

We present the numerical results of the experiments we used to determine the
values of the parameters in our system model for the H$^2$Bird and the ground
station.
